Introducing ICBe: Very High Recall and Precision Event Extraction from Narratives about International Crises

### 2022-07-26 README.Rmd
arXiv submit and readme

[Introducing the ICBe Dataset: Very High Recall and Precision Event Extraction from Narratives about International Crises](https://github.com/CenterForPeaceAndSecurityStudies/ICBEdataset/blob/master/replication_paper/IntroducingICBe_DouglassEtAl_2021_BetaDraft_bookdown.pdf).

The [ArXiv pre-print](https://arxiv.org/abs/2202.07081) was posted on February 15, 2022.

>>>>

[Introducing the ICBe Dataset: Very High Recall and Precision Event Extraction from Narratives about International Crises](https://github.com/CenterForPeaceAndSecurityStudies/ICBEdataset/raw/master/replication_paper/arxiv_draft/paper.pdf) (also available on [ArXiv](https://arxiv.org/abs/2202.07081)).

The v1.1 Online Appendix can be downloaded [here](https://github.com/CenterForPeaceAndSecurityStudies/ICBEdataset/raw/master/replication_paper/arxiv_draft/appendix.pdf).

Version 1.1 is the most recent version and was posted on [ArXiv](https://arxiv.org/abs/2202.07081) on July 26, 2022. Version 1.0 was posted on February 15, 2022.

### 2022-07-26 replication_paper/arxiv_draft/paper.Rmd
can knit!
arXiv submit and readme

#Please provide an abstract of no more than 250 words in a single paragraph. Abstracts should explain to the general reader the major contributions of the article. References in the abstract must be cited in full within the abstract itself and cited in the text.
abstract: |
  How do international crises unfold? We conceptualize of international relations as a strategic chess game between adversaries and develop a systematic way to measure pieces, moves, and gambits accurately and consistently over a hundred years of history. We introduce a new ontology and dataset of international events called ICBe based on a very high-quality corpus of narratives from the International Crisis Behavior (ICB) Project. We demonstrate that ICBe has higher coverage, recall, and precision than existing state of the art datasets and conduct two detailed case studies of the Cuban Missile Crisis (1962) and Crimea-Donbas Crisis (2014). We further introduce two new event visualizations (event icongraphy and crisis maps), an automated benchmark for measuring event recall using natural language processing (sythnetic narratives), and an ontology reconstruction task for objectively measuring event precision. We make the data, replication material, and visualizations of every historical episode available at a companion website www.crisisevents.org.

@@

For our corpus, $D$, we select a set of unusually high-quality historical narratives from the International Crisis Behavior (ICB) project ($n=471$)(SI Appendix, Table A1)[@brecherInternationalCrisisBehavior2017; @brecher_study_1997]. Their domain is 20th and 21st-century crises, defined as a change in the type, or an increase in the intensity, of disruptive interaction with a heightened probability of military hostilities that destabilizes states' relationships or challenges the structure of the international system [@brecherCrisesWorldPolitics1982].^[On near crises see @iakhnisCrisesWorldPolitics2019.] Crises are a significant focus of detailed single case studies and case comparisons because they provide an opportunity to examine behaviors in IR short of, or at least prior to, full conflict  [@holsti1914Case1965; @paigeKoreanDecisionJune1968; @allisonEssenceDecisionExplaining1971; @snyderConflictNationsBargaining1977; @gavinHistorySecurityStudies2014; @georgeDeterrenceAmericanForeign1974; @brecherCrisesWorldPolitics1982; @gaddisExpandingDataBase1987; @brecherPatternsCrisisManagement1988]. Case selection was exhaustive based on a survey of world news archives and region experts, cross-checked against other databases of war and conflict, and non-English sources [@kangUSBiasStudy2019; @brecherInternationalCrisisBehavior2017 p. 59]. Each narrative was written by consensus by a small number of scholars, using a uniform coding scheme, with similar specificity [@hewittEngagingInternationalData2001]. The corpus is unique in IR because it is designed to be used in a downstream quantitative coding project.

@@

@@

>>>>

#Please provide an abstract of no more than 250 words in a single paragraph. Abstracts should explain to the general reader the major contributions of the article. References in the abstract must be cited in full within the abstract itself and cited in the text.
abstract: |
  How do international crises unfold? We conceptualize of international relations as a strategic chess game between adversaries and develop a systematic way to measure pieces, moves, and gambits accurately and consistently over a hundred years of history. We introduce a new ontology and dataset of international events called ICBe based on a very high-quality corpus of narratives from the International Crisis Behavior (ICB) Project. We demonstrate that ICBe has higher coverage, recall, and precision than existing state of the art datasets and conduct two detailed case studies of the Cuban Missile Crisis (1962) and Crimea-Donbas Crisis (2014). We further introduce two new event visualizations (event icongraphy and crisis maps), an automated benchmark for measuring event recall using natural language processing (sythnetic narratives), and an ontology reconstruction task for objectively measuring event precision. We make the data, online appendix, replication material, and visualizations of every historical episode available at a companion website www.crisisevents.org and the github repository.

@@

For our corpus, $D$, we select a set of unusually high-quality historical narratives from the International Crisis Behavior (ICB) project ($n=471$)(SI Appendix, Table A1)[@brecherInternationalCrisisBehavior2017; @brecher_study_1997].^[The Online Appendix is at the [ICBEventData Github Repository](https://urldefense.com/v3/__https://github.com/CenterForPeaceAndSecurityStudies/ICBEventData__;!!Mih3wA!WxDJtEczKfxGTh0S2Krunap8ReymFEL5iTWaSfOHeqlSdyfRx77zmjBSWO1OAm13$).] Their domain is 20th and 21st-century crises, defined as a change in the type, or an increase in the intensity, of disruptive interaction with a heightened probability of military hostilities that destabilizes states' relationships or challenges the structure of the international system [@brecherCrisesWorldPolitics1982].^[On near crises see @iakhnisCrisesWorldPolitics2019.] Crises are a significant focus of detailed single case studies and case comparisons because they provide an opportunity to examine behaviors in IR short of, or at least prior to, full conflict  [@holsti1914Case1965; @paigeKoreanDecisionJune1968; @allisonEssenceDecisionExplaining1971; @snyderConflictNationsBargaining1977; @gavinHistorySecurityStudies2014; @georgeDeterrenceAmericanForeign1974; @brecherCrisesWorldPolitics1982; @gaddisExpandingDataBase1987; @brecherPatternsCrisisManagement1988]. Case selection was exhaustive based on a survey of world news archives and region experts, cross-checked against other databases of war and conflict, and non-English sources [@kangUSBiasStudy2019; @brecherInternationalCrisisBehavior2017 p. 59]. Each narrative was written by consensus by a small number of scholars, using a uniform coding scheme, with similar specificity [@hewittEngagingInternationalData2001]. The corpus is unique in IR because it is designed to be used in a downstream quantitative coding project.

@@

if(fromscratch){

@@

}
